\documentclass{article}
\begin{document}

\section*{Hypothesis}
Will the introduction of a rogue-like level generation complement the horror themes of the game
or will it remove the player from the immersion of the game.

\section*{Goal}
The goal of this prototype is to make a procedural generation algorithm that generates a 
level for the player. 
The algorithm needs to make different rooms that connect to each other while also generating
lights in each rooms. The algorithm will also need to generate a key room which holds a key that
the player needs to pick up, along with a door room which the player needs to bring the key towards.
The algorithm will be considered a success if 
\begin{itemize}
    \item All rooms can be accessed.
    \item The player cannot escape the level.
    \item The key is created correctly.
    \item The door is created correctly.
    \item There are lights in the room.
    \item The enemy AI made in prototype 3 can navigate the level.
    \item The correct generation is consistent.
\end{itemize}

\section*{Challenges}
The general objective of the prototype is to find a key that opens a door in a dungeon like structure, 
while avoiding an enemy AI that is trying to hunt the player.
Some challenges the player may face while trying to complete their objectives
\begin{itemize}
    \item Finding out where the key is.
    \item Evading the enemy.
    \item Hiding from the enemy.
    \item Finding the door that the key unlocks.
\end{itemize}

\section*{Mechanics}
The mechanics that the player can use were shown in previous documents.
Here is a summary of the mechanics that the player can use:
\begin{itemize}
    \item Move with WASD.
    \item Sprint with LShift.
    \item Interact with various game elements through Space.
    \item Toggle the player light with R.
\end{itemize}
\section*{Balance}
The movement mechanic has been balanced in such a way that the base player movement speed is slower
than the base enemy movement speed this is to force the player to use their sprint to get always
or to avoid the enemy entirely. 
The sprint mechanic can only be used for a second just to quickly get away form the enemy this
shows the player that it is better to avoid the enemy than to run from them.
The player can only interact with one interaction at a time this forces the player to drop the item 
they are carrying before interacting with another interaction.
A small cooldown was added to the light toggle to make the player think more of when they
need to toggle their light to hide from the enemy.

\section*{Games with procedural generation}
\subsection*{The Binding of Isaac}
The Binding of Isaac uses a 9x8 grid with each grid cell numbered. The top left grid cell is 0 while
the bottom right cell is 79, this is kept track of with a one dimensional array of 80 length where
the units digit is the x position and the tens digit is the y position on the grid. The algorithm 
for The Binding of Isaac then chooses a random number of rooms to fit in this grid. It always places
the starting room at grid space 35. It then determines the neighbor of the starting room by adding
+1/-1/+10/-10 , if the algorithm can't place a room it gives up. The algorithm keeps track of dead end
rooms which is a room that does not add any neighbors. The algorithm then decides to put special rooms
on the dead end rooms. There are always one of any special room in a level.

I want to take the dead end rooms that only have one entrance and exit and then put then to be either the 
key room or the door room.
\subsection*{Townscaper}

\section*{Different Procedural Generation Algorithms}
These algorithms will help in creating the procedural generation algorithm for the prototype.
\subsection*{Binary Space Partitioning}
Binary Space Partitioning is a technique to generate procedural dungeons. It does this by
recursively dividing a large area into smaller non overlapping areas. 
The algorithm does this by making a single rectangular map then it chooses a random direction
and position along the axis and then splits the rectangular map. It repeats this procedure
until the number of rectangular that you want are met. It also makes sure that it does not
split the rectangles beyond a minimum, thus the rectangles will always have a minimum size.
When the entire rectangle has been split the algorithm then shrinks each rectangle to finish
the level generation.
Pros:
\begin{itemize}
    \item No rooms will overlap.
    \item Rooms are guaranteed to be able to reach each other.
\end{itemize}
Cons:
\begin{itemize}
    \item Can only generate rectangular rooms.
    \item Can not generate hallways between rooms.
\end{itemize}

\subsection*{Wave Function Collapse}
Wave Function Collapse is an algorithm based on constraints. The function ensures consistency
through adjacency rules which determine which tiles can be placed next to each other. The 
function takes a sample input and generates similar to the sample inputs. The functions
picks a cell at random and then collapses it by choosing a random tile. It then chooses
a grid space next to the chosen tile with the least entropy, least amount of tile options.
This process of collapsing repeats until the entire grid is collapsed or a contradiction 
appears when the algorithm cannot find any possible tiles to place down, leading the program
to either backtrack or start from the beginning.
Pros:
\begin{itemize}
    \item Makes natural looking maps.
\end{itemize}
Cons
\begin{itemize}
    \item Takes a lot of processing power
    \item May be prone to contradictions.
\end{itemize}

\section*{Procedural Generation Algorithm}
The algorithm I will make will follow the Binary Space Partitioning first to get the rooms
and their layout. 
Then it will connect the rooms together with hallways. It will do this by choosing a room in the middle 
and branching out. If the distance between two rooms are too big it will not connect the hallway between
them.
The algorithm will keep track of rooms with only one entrance to them and then choose those rooms to
be key or door rooms. If there are not enough single entrance rooms then the algorithm will check which
room has two hallways and then will remove one hallway. If there are not enough two hallway rooms
it will remove from three hallway rooms.
After it has mapped out the rooms and hallways it will then place the tiles for the floor from the tilemap.
After it has placed the floor it will place the walls around the floors.
The algorithm will then place the lights scarcely throughout the map on the floor.
It will also place hiding spots scarcely throughout the map on the walls.

\section*{Macro Design}
The overall goal that the player needs to achieve is to escape. To achieve this goal the player will need
to explore the map to find a key to be able to open the exit. An enemy will chase the player while they are
searching for the key and exit.
The overall story of the game is that the player found themselves in some sort of laboratory and they need to escape.
The player can escape quickly if they follow the voice of the narrator from prototype 1, but if they defy the narrator
it leads the player to the level in prototype 3. The player would then need to escape from their own consequences.
\section*{Process}
Wave Function was not used during the process of making the room generation algorithm.
\section*{Reflection}
\section*{References}
https://www.gamedeveloper.com/game-platforms/how-townscaper-works-a-story-four-games-in-the-making
https://www.boristhebrave.com/2020/09/12/dungeon-generation-in-binding-of-isaac/
https://www.youtube.com/watch?v=zIRTOgfsjl0
https://www.youtube.com/watch?v=3g440SA2hKU
https://www.youtube.com/watch?v=nbi88hY9hcw
https://www.youtube.com/watch?v=hCD0FNVhrIQ
\end{document}