\documentclass{article}
\begin{document}

\section*{Mechanics}
The prototype will be a continuation of the previous prototype
thus the mechanics will be the same as in the previous prototype.
Small overview of the mechanics.
\begin{itemize}
    \item Player can move with WASD.
    \item Player can sprint with LShift.
    \item Player can interact with Space.
    \item Player can toggle light with R.
\end{itemize}
\section*{Challenges}
\subsection*{Player Challenges}
The player will need to use the mechanics to avoid the enemy, while
trying to get their objectives complete. This includes distracting the 
enemy, hiding from the enemy, and moving around the enemy. 
Since the focus of this prototype is on the enemy ai the main challenges
that the player needs to face are challenges based around the enemy ai.

\subsection*{Enemy Challenges}
The enemy will act like a player with different objectives from the actual 
player. The enemy objectives will be to stop the player. The only mechanics
that the enemy has is movement and a director ai that will help it while if the
enemy hits the player they will win.


\section*{Hypothesis}
How will the change of a horror aesthetic to a greybox aesthetic affect how the player 
interacts with the game when the game has a horror game enemy ai and other horror elements? 


\section{Goals}
Make an enemy ai that reacts to the player and changes
its behavior according to the player's actions, which in turn
will change the way that the player reacts to the enemy ai.
Some of these reactions include
\begin{itemize}
    \item Patrolling an area more if the player frequents that area. 
    \item Learning the players next objective and then trying to stop
    the player from completing that objective.
    \item Possibly moving the players next objective to stop them from
    completing it.
\end{itemize}






\section*{Enemy Ai}
The enemy ai will run with a finite state machine, due to the low complexity
of the prototype the finite state machine will work because the number of 
transitions is low between the 3 states.
(What will the speed be of the enemy in each state.)
The Enemy AI will have 3 total senses. One sense to see the player when there
is light, one sense to see the player when there is no light, one sense
to hear the player.
\subsection*{Enemy States}
\subsubsection*{Idle}
The enemy will randomly move around the map.
In this state the enemy will listen for sounds from the player. If any
sound is heard the enemy will go to the position they heard the sound 
and continue idling.
If the enemy is too far from the player the director will send the enemy
closer to the player.
If the enemy is too close to the player for too long then the director
will send the enemy further from the player.
If the enemy sees the player they will enter the chase state.

\subsubsection*{Chase}
The enemy will constantly walk towards the last seen player's position. If the enemy
loses sight of the player they will listen for player sounds and then the
enemy will go to the position of the sound.
If no sound is heard and the enemy can't see the player the enemy will then
enter the guard state. 
If the enemy sees the player enter a hiding spot the enemy will force the player out of the hiding spot.

\subsubsection*{Guard}
If there is an objective that the player must complete nearby the enemy will
move to that objective and then constantly look in an area around that objective.
If there is no objective nearby the enemy will enter the idle state.
If the enemy hears a sound it will move towards that sound and will guard the
area where the sound was heard. The enemy will then move back to the objective
and continue to guard it until the guard time runs out. The enemy will then return
to the idle state when the guard time runs out.

\section*{Director Ai}
The director will be responsible for keeping track of how annoying the enemy
is currently being towards the player, thus the director will know where the
player and enemy is at all times.
This will be done by keeping track of an annoyance meter. 
Certain actions that the enemy does will increase or decrease the annoyance meter.
If the enemy is near the player the annoyance meter will increase while if the enemy
is far from the player the annoyance meter will decrease.
Certain actions the enemy does will increase the annoyance meter. If the enemy is
in the guard state the annoyance meter will go up.
The annoyance meter will not change when the enemy is in the chase state.
If the annoyance meter is full the director will make the enemy walk away from the
player.
If the annoyance meter is empty the director will make the enemy walk towards the
player.
The director will give the enemy nearby player objectives when needed.



\section{Games with dynamic Ai systems}
\subsection*{Alien: Isolation}
There are two parts to the AI in Alien: Isolation that is the Director AI and the
Alien AI. The Director AI knows where the alien and player are at all time, but 
it never communicates this to the Alien AI. 
Alien: Isolation is a horror game thus the player needs to be scared, but if the player
is scared the entire time they would just give up. This lead to the Director keeping track
of a menace meter. The menace meter tells the Director when it should get the Alien to 
back off from the player and allow the player some breathing room and time to progress.
The Alien AI can only act on what it senses, this leads the AI feel like its hunting the
player. This is due to the Alien not moving around optimally and taking its time to move
to its destination. 
The Alien can also respond to the player's action if the player makes too much noise and if
the Alien is close enough to sense that noise.
The Alien has different sensors, visual, auditory and touch. The Alien acts on these senses
to try and kill the player.
The Alien Ai is made form a behavior tree.

The parts of Alien: Isolation that I will use in my game will be the similar to the Director AI
and the Alien AI. I will have the Director Ai keep track of an annoyance meter and direct an Enemy
Ai to and away from the player. The Enemy will have a sound sensor and a vision range which it will
use to defeat the player. Unlike the Alien AI which uses a behavior tree the Enemy Ai in the prototype
will use a finite state machine. This is because recreating a behavior tree needs a lot of conditions
just to get to the behavior that the AI needs to do at the moment and if made incorrectly can worsen
performance. The finite state machine can get complex if there are too many states, but this will
not happen due to only 3 states being planned for the prototype.




https://www.aiandgames.com/p/revisiting-alien-isolation
https://www.gamedeveloper.com/design/the-perfect-organism-the-ai-of-alien-isolation
https://www.gamedeveloper.com/programming/behavior-trees-for-ai-how-they-work
https://blog.littlepolygon.com/posts/fsm/

\section{Micro Design}
The enemy ai will cause moment to moment gameplay by influencing the
player's decision making through the enemy behavior. This will cause
the player to either avoid certain areas or delay doing certain tasks
because the enemy is currently obstructing those game elements.
The player mechanics will be refined to give more feedback to the
player that they are currently using a mechanic.

\section*{Process}
StateMachine for the enemy is being made while following the layout of the youtube videos.
Senses for enemy is being made. 3 Senses have been decided on. Light sense which is what the
enemy can see when it is light. Dark sense which is what the enemy can see when there is no light.
Always sense which is what the enemy can always see.

During the development of the enemy, when the player is hiding in a hiding spot and the enemy is nearby
the Director will try to send the enemy away, but because the random spot the director chooses to send
the enemy away to can be outside of the NavMesh causing the enemy to move near the player. This gives the
idea that the enemy is searching the area for the player.

Sound manager is being made while following the youtube video. Some changes from the video will be made.

\section*{Reflection}



https://www.youtube.com/watch?v=RQd44qSaqww
https://www.youtube.com/watch?v=iOYo7flBUW4
https://www.youtube.com/watch?v=j1-OyLo77ss
https://www.youtube.com/watch?v=DU7cgVsU2rM
\end{document}